Make any stupid plot you want

### 2021-01-07 draft/sections/math.tex
going in circles here

\section{Notation \& Definitions}
In this section we introduce a mathematical description of the visualization pipeline where artist $A$ functions transform data of type $\Gamma(E)$ to an intermediate representation in prerendered display space of type $\Gamma(H)$:

@@

\begin{itemize}
\item $A$ is the function that converts an instance of data $\Gamma(E)$ to an instance of a visual representation $\Gamma(H)$ 
\item $E$ is a locally trivial fiber bundle over $K$ representing data space.
\item $K$ is a triangulizable space encoding the connectivity of the points in $E$
\item $H$ is a fiber bundle over $S$ representing visual space
\item $S$ is a simplacial complex encoding the visualization
\item $\Gamma$ is the global space of sections
\end{itemize}

When $E$ is a trivial fiber bundle $E = F \times K$, it can be assumed that all fibers $F_{k}$ over $k \in K$ are equal. Fiber bundles are product spaces of toplological spaces, which are a set of points with a set of neighborhoods for each point\cite{FiberBundle2020, rowlandFiberBundle}.

\subsection{Fiber Bundles}
We provide a brief description of fiber bundles because we model data, visual transformations, and a prerendered visual graphic as fiber bundles. A fiber bundle is a structure $(E, B, \pi, F)$  consisting of topological total space $E$, base space $K$, fiber space $F$ and the map from total space to base space:

@@

\subsubsection{Base space}
\begin{figure}[H]
    \label{fig:base_space}
    \includegraphics[width=0.4\linewidth]{figures/sections/math/k_qspace.png}
\end{figure}

@@

As shown in figure~\ref{fig:kquote}, the fibers $F$ divide $E$ into smaller spaces consisisting of $F$ and an open set neighborhood around $F$. This subdivision is projected down to the toplology $\mathcal{T}$

\begin{equation}
    \label{eq:base_space}
\mathcal{T}_b = \{U\subseteqq B: \{p \in E: [p] \in U\}\in \mathcal{T}_E\}
\end{equation}

where $[p] \in U$ is the point $b \in B$ with an open set surrounding it that has an open preimage in $E$ under the surjective map $\pi: p \rightarrow [p]$.

\subsubsection{Fiber}
As shown in equation!\ref{eg:base_space}, every point $b \in B$ has a local open set neighborhood $U$ \cite{FiberBundle2020, rowlandFiberBundle}

\begin{equation}
    \label{eq:fiber_local_trivial}
    \begin{tikzcd}
        \pi^{-1}(U) \arrow[r, "\varphi"] \arrow[d, "\pi"'] & U \times F \arrow[ld, "\mathrm{proj}_U"] \\
        U                                                  &                                         
    \end{tikzcd}
\end{equation}
such that $\varphi: \pi^{-1}(U) \rightarrow U \times F$ is a homeomorphism where $\pi$ and $\mathrm{proj}_U$ both map to $U$ and the fiber over $k$ $F_b = \pi^{-1}({b \in B}) $ is homomorphic to the fiber $F$.

\subsubsection{Section}
The section $f$ is the mapping from base space to total space $f: B\rightarrow E$ 
\begin{equation}
    \label{eq:section}
    \begin{tikzcd}
        F \arrow[r, hook] & E \arrow[d, "\pi"']           \\
        & B \arrow[u, "f"', bend right]
    \end{tikzcd}
\end{equation}

@@

where the domain of $g(b)$ is $F_b$ and returns a point $p$ in $F_b$. The space of all possible sections $f$ of $E$ is $\Gamma(E)$. All sections $f \in \Gamma(E)$ have the same fibers $F$ and connectivity $B$.

\subsubsection{Sheaf and Stalk}
As described in equation~\ref{eq:local_trivial}, there is a local space $U \subset B$ around every $b$. The inclusion map $\iota: U \rightarrow B$ can be pulled back such that $\iota^{*}E$ is the space of $E$ restricted over $U$. 
\begin{equation}
    \label{eq:sheaf}
    \begin{tikzcd}
        \iota^*E \arrow[d, "\pi"']           & E \arrow[d, "\pi"'] \arrow[l, "\iota^*"']         \\
        U \arrow[u, "\iota^*f"', bend right] & B \arrow[u, "f"', bend right] \arrow[l, "\iota"']
        \end{tikzcd}
\end{equation}

The localized section of fibers $\iota^*f: U \rightarrow \iota^*E$ is the sheaf $\mathcal{O}(E)$ with germ of $\xi^*f$. The neighborhood of points the sheaf lies over is the stalk $\mathcal{F}_b$ \cite{StalkSheaf2019,spanier1989algebraic}

\begin{equation}
    \label{eq:stalk}
    \iota^{-1}\mathcal{F}(\{b\}) = \varinjlim_{b\subseteq U}\mathcal{F}(U) =  \varinjlim_{b \in U} = \mathcal{F}_b 
\end{equation}

which through $\iota$ gets the data in $E$ at and near to $b$. Restricting the artist to the sheaf means the artist knows the data in $F$ and also has access to derivatives of the data. This property is useful for some visual transformations. 
%% gives all direvatives but we need the jet which is Add stuff about jets

\subsection{Data Model}
As proposed by Butler \cite{butlerVectorBundleClassesForm1992,butlerVisualizationModelBased1989}, we model data as a fiber bundle (E, K, $\pi$, F) with $\pi: E \rightarrow K$ where $K$ which can be thought of as a set of keys $k$. A section $\tau:K \rightarrow E$ is an instance of the data that lies in $E$ and is discussed in section~\ref{sec:data_fiber}.

\subsubsection{Example}

\begin{figure}[H]
    \label{fig:data_fiber_bundle}
    \includegraphics[width=.2\linewidth]{figures/sections/math/fiberbundle.png}
    \caption{write up some words here}
\end{figure}

As illustrated by figure~\ref{fig:fiberbundle}, the vertical lines $F$ are the range of possible temperature values embedded in the total space $E$. The base space $K$ of the fiber bundle is a line because the data points $r$ in $E$ are on a space that is  continous in one dimension.

\subsubsection{Base Space}
The base space $K$ is a representation of the connectivity of the data, specifically whether the points in $E$ are discrete or sampled from a continous space. The same dataset can be expressed with different $K$.

% replace this table w/ a diagram that shows this 
\begin{description}
    \item[0-simplex] discrete observations (inventory records)
    \item[1-simplex] 1D continuos data (timeseries)
    \item[2-simplex] 2D continuos data (map)
    \item[3-simplex] 3D continuos data (video)
\end{description}

\subsubsection{Example}
\begin{figure}[ht]
    \includegraphics[width=0.2\linewidth]{figures/sections/math/temp_1k.png}
    %% add box around neighboring P and Map
    \label{fig:k_data}
\end{figure}

\subsubsection{Fiber and Sections}
\label{sec:data_fiber}
We use Spivak's formalization of data base schemas as the basis of our fiber space $F$ \cite{spivakSIMPLICIALDATABASES}. He defines the type specification 
\begin{equation}
\pi: U \rightarrow DT
\end{equation}

where $DT$ is the set of data types (as identified by their names) and $U$ is the disjoint set of all possible objects $x$ of all types in $DT$. This means that for each type $T\in DT$, the preimage $\pi^{-1}(T)\subset U $ is the domain of $T$, and $x \in \pi^{1}(T)\subset U$ is an object of type $T$. Spivak then defines a schema $(C, \sigma)$ of type $\pi$, where $\pi$ is the universe of all types, such that 
\begin{equation}
\sigma: C \rightarrow DT
\end{equation}
where $C$ is the finite set of names of columuns, which we generalize to data fields in $E$. The set of all values restricted to the datatypes in $DT$ is $U_{\sigma}$

\begin{equation}
    \begin{tikzcd}
        U_{\sigma} \arrow[d, "\pi_{\sigma}"'] \arrow[r] & U \arrow[d, "\pi"] \\
        C \arrow[r, "\sigma"]                           & DT                
    \end{tikzcd}
\end{equation}
The pullback $U_{\sigma} \coloneqq \sigma^{-1}(U)$ restricts $U$ to the datatypes of the fields in $C$ such that $U_{\sigma}$ is the fiber product $U \times_{DT} C$, and the pullback $\pi_{\sigma}:U_{\sigma} \rightarrow C$ specifies the domain bundle $U_{\sigma}$ over $C$ induced by $\sigma$. The fiber $F$ is the cartesian product of all sets in the disjoint union $U_{\sigma}$.

@@

\subsection{Prerender Space}
\label{sec:display}
We model the prerender space on which lives on ideal version of the visulaization as a fiber bundle (H, S, $\pi$, D). $H$ is the predisplay space, with a fiber $D$ dependent on the target physical display and a base space of $S$.

\subsubsection{Base space}
$K$ can be considered a subspace of the screen base space $S$ such that $\xi: S \rightarrow K$ is a deformation retraction \cite{RetractionTopology2020}
\begin{equation}
    \begin{tikzcd}
        E \arrow[d, "\pi"'] & H \arrow[d, "\pi"'] \\
        K                   & S \arrow[l, "\xi"']
        \end{tikzcd}
\end{equation}

@@

\subsubsection{Fiber and Section}
A section $\rho: S \rightarrow H$ is a mapping from a region $s$ on a mathematical encoding of the image to a region $xy$ on the screen that the renderer then maps to visual space as defined in D. For a physical screen display, the predisplay space is a trivial fiber bundle $H=\mathbb{R}^{7}\times S$ such that $\rho$ is
\begin{equation}
    \rho(s)  = \{x, y, z, r, g, b, a\}
    \label{eq:rho}
\end{equation}

@@

Here we assume a single opaque 2D image such that the $z$ and $alpha$ fields can be omitted.

@@

\subsection{Artist}

@@

\begin{equation}
    \label{eq:artist}
\begin{tikzcd}
    E \arrow[r, "\nu"] \arrow[rd, "\pi"'] & V \arrow[d, "\pi"] & \xi^*V \arrow[r, "Q"] \arrow[d, "\xi^*\pi"'] & H \arrow[ld, "\pi"] \\
                                          & K                  & S \arrow[l, "\xi"']                          &                    
\end{tikzcd}
\end{equation}

@@

\subsubsection {Example: Matplotlib Visual Fiber}
For example, for Matplotlib \cite{hunterMatplotlib2DGraphics2007}, some of the possible types in $P$ are:
\begin{table}[ht]
    \label{tab:mpl_visual_variable_fiber}
    \renewcommand{\arraystretch}{2}
    \begin{tabulary}{\textwidth}{|l|L|l|}\hline
     $\bm{\nu_{i}}$                      & $\bm{\mu_{i}}$                                                            & $\bm{codomain(\nu_{i})}$  \\ \hline                                              
    position                    & x, y, z, theta, r                                                          & $\mathbb{R}$   \\ \hline
    size                        & linewidth, markersize                                            & $\mathbb{R}^{+}$   \\ \hline
    shape                       & markerstyle                                                      & $\{f_{0}, \ldots, f_{n}\}$ \\ \hline
    color                       & color, facecolor, markerfacecolor, edgecolor  & $\mathbb{R}^{4}$ \\ \hline
    \multirow{2}{*}{texture}    & hatch                                                            & $\mathbb{N}^{10}$\\\cline{2-3}
                                & linestyle                                                        & $\{f_{0}, \ldots, f_{n}\} \times (\mathbb{R}, \mathbb{R^+}^{n, n\%2=0})$ \\ \hline              
    \end{tabulary}
\end{table}

\subsubsection{Visual Channels}
$\nu: E \rightarrow V$ is an equivariant map such that there is a homomorphism from left monoid actions on $E_{i}$ to left monoid actions on $V_{i}$ where $i$ identifies a field in the fiber. $E_i$ and $V_{i}$ each contain a set of values as defined in $F$ and $P$ respectively. A validly constructed $\nu$ is one where the  diagram 
\begin{equation}
    \label{eq:nu_categorical}
\begin{tikzcd}
    E_i \arrow[r] \arrow[r, "\nu_i"] \arrow[d, "m_e"'] & V_i \arrow[d, "m_v"] \\
    E_i \arrow[r, "\nu_i"]                           & V_i               
\end{tikzcd}
\end{equation}
commutes such that $\nu_i(m_e(E_i)) = m_v(\nu_i(E_i))$.

@@

\paragraph{Example: Translation}
\textbf{fairly certain I lost the thread here}
According to Stevens, interval data is a set with general linear group actions \cite{stevensTheoryScalesMeasurement1946,leaFormalizationMeasurementScale}. Position is a visual variable that can support translation \cite{bertinIIPropertiesGraphic2011,krygierMakingMapsVisual2005,munznerMarksChannels}.

For example, here $\nu$ is a direct map $\nu(\tau_{i,k}) = \mu{i,k}$ and the transform function is a multiplicative shift $t(x) = x + x$ applied twice

\begin{align}
    \nu(t(t(\tau_{i,k}))) &= t(t(\nu(\tau_{i,k})))\\
    \nu(t(2\tau_{i,k})) &= t(t_v(\mu_{i,k}))\\
    \nu(2\tau_{i,k} + 2\tau_{i,k}) &= t(2\mu_{i,k})\\
    \nu(4\tau_{i,k}) &= 2\mu_{i,k} + 2\mu_{i,k} \\
    \nu(4\tau_{i,k})&=4\mu_{i,k}\\
    4\mu_{i,k}&=4\mu_{i,k}\\
\end{align}
$\nu$ is valid because scaling the data by a factor of 4 causes a scaling of the equivalent visualization by 4, which since the constant factor can be pulled out means they are equivalent.

\paragraph{Example: Invalid $\nu$}
Given a transform $t(x) = 2*x$, we construct a $\nu$ that always takes data to .5: 
\begin{equation}
    \label{eq:nu_equation_bad}
    \begin{tikzcd}
        E_1 \arrow[r] \arrow[r, "\lambda:e\mapsto.5"] \arrow[d, "2e"'] & V_i \arrow[d, "2v"] \\
        E_1 \arrow[r, "\lambda"]                                        & V_1                 
    \end{tikzcd}
\end{equation}

@@

For each region $s$ in the display space $H$, the mark  \cite{bertinIIPropertiesGraphic2011,carpendaleVisualRepresentationSemiology} it belongs to can be found by mapping $s$ back to $K$ via the lookup on $S$ then taking $\xi(s)$ back to a point on $k \in K$ which lies on the path connected component $J \subset K$. 
\begin{equation}
    \begin{tikzcd}
        H \arrow[r, shift left] & S \arrow[l, "\rho(\xi^{-1}(J))", shift left] \arrow[rr, "\xi(s)", shift left] &  & J_{k} =  \{j \in K \text{ s. t. } \exists \gamma \text{ s.t. } \gamma(0)=k \text{ and }\gamma(1)=j\} \arrow[ll, "\xi^{-1}(J)", shift left]
    \end{tikzcd}
    \label{eq:mark}
\end{equation}
where the path\cite{ConnectedSpace2020}  $\gamma$ from $k$ to $j$ is a continous function from the interval [0,1]. To get back to the display space $H$ from $J$, the inverse image of $J \in S, \xi^{-1}(J)$ is pushed back to $S$, and then $\rho(\xi^{-1}(J))$ maps it into $R^{7}$ such that $Q\circ\xi^*\mu(\xi^{-1}(J))$ generates a graphical mark.

>>>>

%% convention is base space \times fiber bundle
%% change B to K
\section{Notation \& Definitions}
%% intro placeholder of eq in intro
%% use let or where before you introduce symbols
%% more notations w/ general words 
%% tone down - mathcal A, mathcal E, and mathcal H - space, will formalized in this section 
%% give the why of the math after every mention of why
In this section we introduce a mathematical description of the visualization pipeline where artist $A$ functions transform data of type $\Gamma(E)$ to an intermediate representation in prerendered display space of type $\Gamma(H)$:

@@

\begin{itemize}
\item $A$ is the function that converts an instance of data $\Gamma(E)$ to an instance of a visual representation $\Gamma(H)$ 
\item $E$ is a locally trivial fiber bundle over $K$ representing data space.
\item $H$ is a fiber bundle over $S$ representing visual space
\item $K$ and $S$ is a triangulizable topological space or CW complex encoding the connectivity of the points in $E$
\end{itemize}
All the fiber bundles mentioned in this work is assumed to be locally trivial \cite{rowlandFiberBundle,FiberBundle2020}.

\subsection{Data Fiber Bundles}
\begin{figure}[H]
    \label{fig:data_fiber_bundle}
    \includegraphics[width=.2\linewidth]{figures/sections/math/fiberbundle.png}
    \caption{write up some words here}
\end{figure}

As proposed by Butler \cite{butlerVectorBundleClassesForm1992,butlerVisualizationModelBased1989}, we model data as a fiber bundle (E, K, $\pi$, F) with $\pi: E \rightarrow K$ where $K$ which can be thought of as a set of keys $k$. A section $\tau:K \rightarrow E$ is an instance of the data that lies in $E$ and is discussed in section~\ref{sec:data_fiber}.

We provide a brief description of fiber bundles because we model data, visual transformations, and a prerendered visual graphic as fiber bundles.  Fiber bundles are product spaces of toplological spaces, which are a set of points with a set of neighborhoods for each point\cite{FiberBundle2020, rowlandFiberBundle}. A fiber bundle is a structure $(E, B, \pi, F)$  consisting of topological total space $E$, base space $K$, fiber space $F$ and the map from total space to base space:

@@

\subsubsection{Base space}
\begin{figure}[H]
    \label{fig:base_space}
    \includegraphics[width=0.4\linewidth]{figures/sections/math/k_qspace.png}
    %%include second figure where fiber goes otherway
\end{figure}

%%% add in motivation - encodes the connectiveity of the points, choice of split is intrinsinc to how we want to view the data

@@

As shown in figure~\ref{fig:kquote}, the fibers $F$ divide $E$ into smaller spaces consisisting of $F$ and an open set neighborhood \cite{FiberBundle2020, rowlandFiberBundle}  around $F$.
%%so why topology? 
\paragraph{Example}
%%% pull up data structures like discrete, continous, etc w/ base space 
%%% little drawing dots, line, plane, cube

\begin{figure}[ht]
    \includegraphics[width=0.2\linewidth]{figures/sections/math/temp_1k.png}
    %% add box around neighboring P and Map
    \label{fig:k_data}
\end{figure}

\subsubsection{Fiber}
%% pull fiber stuff up here? what is it? why? fiber as cartesian product of sets
%% actual values are in the fiber 
%% gonna view spaces as simple piece put together 
%% Our fibers are cross products of (column name, domain) as described by Spivak's \cite{spivakSIMPLICIALDATABASES}.

\begin{equation}
    \label{eq:fiber_local_trivial}
    \begin{tikzcd}
        \pi^{-1}(U) \arrow[r, "\varphi"] \arrow[d, "\pi"'] & U \times F \arrow[ld, "\mathrm{proj}_U"] \\
        U                                                  &                                         
    \end{tikzcd}
\end{equation}
such that $\varphi: \pi^{-1}(U) \rightarrow U \times F$ is a homeomorphism where $\pi$ and $\mathrm{proj}_U$ both map to $U$ and the fiber over $k$

%% rewrite this section - what are the goals here and why should we care? 
%% devoid of any context

$F_b = \pi^{-1}({b \in B}) $ is homomorphic to the fiber $F$.
%% add a sentence for why we care
%% fibers are cartesian products of these typles sets (name, domain, monoidal action)

%%the break out more about how fibers are cross products and what that means and how that's the structure - pull the monoids definitions here

\paragraph{Example}
%% stevens scales are examples of this 
%% one ecample of F1 is (names, strings, concat), (ordinal, Z,  ordering), ()

\subsubsection{Section}
%% add context
The section $f$ is the mapping from base space to total space $f: B\rightarrow E$ 
\begin{equation}
    \label{eq:section}
    \begin{tikzcd}
        F \arrow[r, hook] & E \arrow[d, "\pi"']           \\
        & B \arrow[u, "f"', bend right]
    \end{tikzcd}
\end{equation}

@@

where the domain of $g(b)$ is $F_b$ and returns a point $p$ in $F_b$. The space of all possible sections $f$ of $E$ is $\Gamma(E)$. All sections $f \in \Gamma(E)$ have the same fibers $F$ and connectivity $B$. 
\paragraph{Example}
%%talk about table and all that jazz

@@

\subsubsection{Sheaf and Stalk}
%% add motivation - zoom, subsection, streaming, also for realizing visualization, restricting to that piece - need to know near point w/o 
As described in equation~\ref{eq:local_trivial}, there is a local space $U \subset B$ around every $b$. The inclusion map $\iota: U \rightarrow B$ can be pulled back such that $\iota^{*}E$ is the space of $E$ restricted over $U$. 
\begin{equation}
    \label{eq:sheaf}
    \begin{tikzcd}
        \iota^*E \arrow[d, "\pi"']           & E \arrow[d, "\pi"'] \arrow[l, "\iota^*"']         \\
        U \arrow[u, "\iota^*f"', bend right] & B \arrow[u, "f"', bend right] \arrow[l, "\iota"']
        \end{tikzcd}
\end{equation}

The localized section of fibers $\iota^*f: U \rightarrow \iota^*E$ is the sheaf $\mathcal{O}(E)$ with germ of $\xi^*f$ which is the localized section. The neighborhood of points the sheaf lies over is the stalk $\mathcal{F}_b$ \cite{StalkSheaf2019,spanier1989algebraic} which is a ...$\dots$
. Restricting the artist to the sheaf means the artist knows the data in $F$ and also has access to derivatives of the data. This property is useful for some visual transformations. 
%% gives all direvatives but we need the jet which is Add stuff about jets

\subsubsection{Triangulization}
%%drop down to after the fiber section
The base space $K$ is a representation of the connectivity of the data, specifically whether the points in $E$ are discrete or sampled from a continous space. The same dataset can be expressed with different $K$.

\paragraph{Example}
chopping up a torus maybe? talk about how that gets unpacked into triangles and then into vertices

\subsection{Prerender Space}
\label{sec:display}

We model the prerender space on which lives on ideal version of the visulaization as a fiber bundle (H, S, $\pi$, D). $H$ is the predisplay space, with a fiber $D$ dependent on the target physical display and a base space of $S$.

\subsubsection{Base space}
%%pull up to the very top that dim(k) < screen space, need to thicken therefore S
$K$ can be considered a subspace of the screen base space $S$ such that $\xi: S \rightarrow K$ is a deformation retraction \cite{RetractionTopology2020}
\begin{equation}
    \begin{tikzcd}
        E \arrow[d, "\pi"'] & H \arrow[d, "\pi"'] \\
        K                   & S \arrow[l, "\xi"']
        \end{tikzcd}
\end{equation}

@@

\subsubsection{Fiber and Section}
A section $\rho: S \rightarrow H$ is a mapping from a region $s$ on a mathematical encoding of the image to a region $xy$ on the screen that the renderer then maps to visual space as defined in D.

\paragraph{Example}
For a physical screen display, we can consider a predisplay space that is a trivial fiber bundle $H=\mathbb{R}^{5}\times S$ such that $\rho$ is
\begin{equation}
    \rho(s)  = [x(s), y(s), r(s), g(s), b(s)]
    \label{eq:rho}
\end{equation}

@@

Here we assume a single opaque 2D image such that the $z$ and $alpha$ fields can be omitted. To support overplotting and transparency, we consider $D=R^{7}$
%%H can be other spaces

@@

\subsection{Artist}
%%introduce O(E) up in previous section, then refer back to that section

@@

\begin{equation}
    \label{eq:artist}
    \begin{tikzcd}
        E \arrow[r, "\nu"] \arrow[rd, "\pi"'] & V \arrow[d, "\pi"] & \xi^*V \arrow[r, "Q"] \arrow[d, "\xi^*\pi"'] \arrow[l, "\xi^*"'] & H \arrow[ld, "\pi"] \\
                                              & K                  & S \arrow[l, "\xi"']                                              &                    
        \end{tikzcd}
\end{equation}
%%map backwords via pullback can copy values over k over and over to corresponding S_k

@@

\subsubsection {Example: Matplotlib Visual Fiber}
For example, for Matplotlib \cite{hunterMatplotlib2DGraphics2007}, some of the possible types in $P$ are:
\begin{table}[ht]
    \label{tab:mpl_visual_variable_fiber}
    \renewcommand{\arraystretch}{2}
    \begin{tabulary}{\textwidth}{|l|L|l|}\hline
     $\bm{\nu_{i}}$                      & $\bm{\mu_{i}}$                                                            & $\bm{codomain(\nu_{i})}$  \\ \hline                                              
    position                    & x, y, z, theta, r                                                          & $\mathbb{R}$   \\ \hline
    size                        & linewidth, markersize                                            & $\mathbb{R}^{+}$   \\ \hline
    shape                       & markerstyle                                                      & $\{f_{0}, \ldots, f_{n}\}$ \\ \hline
    color                       & color, facecolor, markerfacecolor, edgecolor  & $\mathbb{R}^{4}$ \\ \hline
    \multirow{2}{*}{texture}    & hatch                                                            & $\mathbb{N}^{10}$\\\cline{2-3}
                                & linestyle                                                        & $\{f_{0}, \ldots, f_{n}\} \times (\mathbb{R}, \mathbb{R^+}^{n, n\%2=0})$ \\ \hline              
    \end{tabulary}
\end{table}
%%needs context, pulling monoids up gives it
\subsubsection{Visual Channels}
$\nu: E \rightarrow V$ is an equivariant map such that there is a homomorphism from left monoid actions on $E_{i}$ to left monoid actions on $V_{i}$ where $i$ identifies a field in the fiber. $E_i$ and $V_{i}$ each contain a set of values as defined in $F$ and $P$ respectively. A validly constructed $\nu$ is one where the  diagram 
\begin{equation}
    \label{eq:nu_categorical}
\begin{tikzcd}
    E_i \arrow[r] \arrow[r, "\nu_i"] \arrow[d, "m_e"'] & V_i \arrow[d, "m_v"] \\
    E_i \arrow[r, "\nu_i"]                           & V_i               
\end{tikzcd}
\end{equation}
commutes such that $\nu_i(m_e(E_i)) = m_v(\nu_i(E_i))$.

@@

\paragraph{Example: Translation}
\textbf{fairly certain I lost the thread here}
According to Stevens, interval data is a set with general linear group actions \cite{stevensTheoryScalesMeasurement1946,leaFormalizationMeasurementScale}. Position is a visual variable that can support translation \cite{bertinIIPropertiesGraphic2011,krygierMakingMapsVisual2005,munznerMarksChannels}. 
\begin{equation}
\nu(x + c) = \nu(x) + \nu(c)
\end{equation}

\paragraph{Example: Invalid $\nu$}
Given a transform $t(x) = x+2$, we construct a $\nu$ that always takes data to .5: 
\begin{equation}
    \label{eq:nu_equation_bad}
    \begin{tikzcd}
        E_1 \arrow[r] \arrow[r, "\lambda:e\mapsto.5"] \arrow[d, "2e"'] & V_i \arrow[d, "2v"] \\
        E_1 \arrow[r, "\lambda"]                                        & V_1                 
    \end{tikzcd}
\end{equation}

@@

For each region $s$ in the display space $H$, the mark  \cite{bertinIIPropertiesGraphic2011,carpendaleVisualRepresentationSemiology} it belongs to can be found by mapping $s$ back to $K$ via the lookup on $S$ then taking $\xi(s)$ back to a point on $k \in K$ which lies on the path connected component $J \subset K$.

%% defined J_{k} first, then pull down to here, then can do \rho S_j
\begin{equation}
    \begin{tikzcd}
        H \arrow[r, shift left] & S \arrow[l, "\rho(\xi^{-1}(J))", shift left] \arrow[rr, "\xi(s)", shift left] &  & J_{k} =  \{j \in K \text{ s. t. } \exists \gamma \text{ s.t. } \gamma(0)=k \text{ and }\gamma(1)=j\} \arrow[ll, "\xi^{-1}(J)", shift left]
    \end{tikzcd}
    \label{eq:mark}
\end{equation}
where the path\cite{ConnectedSpace2020}  $\gamma$ from $k$ to $j$ is a continous function from the interval [0,1]. To get back to the display space $H$ from $J$, the inverse image of $J \in S, \xi^{-1}(J)$ is pushed back to $S$, and then $\rho(\xi^{-1}(J))$ maps it into $R^{7}$ such that $Q\circ\xi^*\mu(\xi^{-1}(J))$ generates a graphical mark.
